\LARGE \bf Detection of design pattern : A systematic mapping study

### 2015-12-31 article/main.tex
modified:   main.tex/correction

Design partterns are best pratices proposed by the Gang of Four in their seminal
book to recurring design problems.

@@

Detection of design patterns in software has been a relatively active research
interest of the past decade in software engineering.
Proposed methods of automatic detection aims in part to facilitate the work of
developpers in understanding a piece of software through reverse engineering.

@@

No studies have been conducted to analyse the trends of the field.

@@

We decided to query only one database, Scopus \cite{c2}, that claims to be the
largest abstract and citation database of peer-reviewed literature.
It indexes the main Computer Science databases : Springer, IEEE, ACM and
others.
The main advantage of using Scopus is that it provides a functionnality to
export the result of a search query on its database.
Some of those exported results would not have been easily obtainable on some
publishers search engines that do not provide an export functionnality.
Consequently, Scopus was used mostly as a Search and Export portal over the
relevant publications, greatly reducing the effort needed to extract the
original articles set. 
% TODO: Original articles set <- better wording?!

From the two research questions we tried to maximise the number of publications
found on the subject.
% Thesaurus is a synonym dictionnary... therefore a "disjunction of thesaurus"
% doesn't make any sense.
To achieve that purpose we used for the query a disjonction of thesaurus for
\textit{detection} on their respective contracted form : \textit{detect*},
\textit{recogni*} and \textit{ident*}.
We have then added to the query a disjonction of \textit{pattern} and \textit{motif}.
The query was limitied to the abstract, the title, and keywords of each article.
% Do we like oxford comma?

@@

The query resulted in a total of 403 articles.
Of those articles, we found two duplicates that were immediately removed from
the set of articles to analyse which brings down the number of articles for
screening to 401.

@@

It is usually said that a Cohen's kappa coefficient of more than $0.7$ indicate
a good agreeement.% citation needed

@@

\begin{itemize}
  \item \textbf{Detection strategy}:
    This determine the means on which the detection is based.
    Possible values: Artificial intelligence, Logic/Formalisation, Graph,
    Metric, Automata, Instrumentation/profiling and Others.

  \item \textbf{Language dependance}:
    This category aims to classify detection methods on wether it is dependant
    on the language or not. 
    Possible values: Dependant or Independant
% This  specifies if the detection is langage dependent or independent,

@@

  \item \textbf{Detected pattern types}:
    This characterizes the type of design pattern a specific detection method
    can manage.
    The possible values for this category are Creationnal, Behavioural,
    Structural and Not specified.

@@

\begin{center}
  \begin{tabular}{ lll }
    \bf Category & \bf Class & \bf \# of articles \\
    \hline
    \multirow{7}{*}{Detection Srategy}
    & \multicolumn{1}{l}{AI}           & \multicolumn{1}{l}{11} \\
    & \multicolumn{1}{l}{Logic}        & \multicolumn{1}{l}{22} \\
    & \multicolumn{1}{l}{Graph}        & \multicolumn{1}{l}{15} \\
    & \multicolumn{1}{l}{Metric}       & \multicolumn{1}{l}{7} \\
    & \multicolumn{1}{l}{Automata}     & \multicolumn{1}{l}{1} \\
    & \multicolumn{1}{l}{Instr./Prof.} & \multicolumn{1}{l}{10} \\
    & \multicolumn{1}{l}{Pattern Mathching}
                                       & \multicolumn{1}{l}{8} \\
    & \multicolumn{1}{l}{Others}       & \multicolumn{1}{l}{23} \\
    \hline
    \multirow{2}{*}{\textbf{Language Dependance}}
    & \multicolumn{1}{l}{Dependant}    & \multicolumn{1}{l}{XXX} \\
    & \multicolumn{1}{l}{Independant}  & \multicolumn{1}{l}{XXX} \\
    \hline
    \multirow{3}{*}{\textbf{Analysis Type}}
    & \multicolumn{1}{l}{Static}       & \multicolumn{1}{l}{XXX} \\
    & \multicolumn{1}{l}{Dynamic}      & \multicolumn{1}{l}{XXX} \\
    & \multicolumn{1}{l}{Hybrid}       & \multicolumn{1}{l}{XXX} \\
    \hline
    multirow{3}{*}{Detection Level}
    & \multicolumn{1}{l}{Execution}    & \multicolumn{1}{l}{8} \\
    & \multicolumn{1}{l}{Source}       & \multicolumn{1}{l}{44} \\
    & \multicolumn{1}{l}{Model}        & \multicolumn{1}{l}{7} \\
    \hline
    \multirow{2}{*}{Pattern detection generality}
    & \multicolumn{1}{l}{Specific}     & \multicolumn{1}{l}{XXX} \\
    & \multicolumn{1}{l}{General}      & \multicolumn{1}{l}{XXX} \\
    \hline
    \multirow{4}{*}{Detected Pattern Types}
    & \multicolumn{1}{l}{Creationnal}  & \multicolumn{1}{l}{23} \\
    & \multicolumn{1}{l}{Structural}   & \multicolumn{1}{l}{34} \\
    & \multicolumn{1}{l}{Behaviour}    & \multicolumn{1}{l}{49} \\
    & \multicolumn{1}{l}{Other/Not Specified}
                                       & \multicolumn{1}{l}{17} \\
    \hline
    \multirow{6}{*}{Validation Method}
    & \multicolumn{1}{l}{Benchmark}    & \multicolumn{1}{l}{7} \\
    & \multicolumn{1}{l}{Case Study}   & \multicolumn{1}{l}{40} \\
    & \multicolumn{1}{l}{Experiment}   & \multicolumn{1}{l}{8} \\
    & \multicolumn{1}{l}{Survey}       & \multicolumn{1}{l}{0} \\
    & \multicolumn{1}{l}{Other}        & \multicolumn{1}{l}{1} \\
    & \multicolumn{1}{l}{None}         & \multicolumn{1}{l}{11}
  \end{tabular}
\end{center}

@@

This could indicate either that the field is mature and that research avenues
have been exhaused, that the field currently hit a roadblock, or that interest
is fading due to a lack of interest in the need for design pattern detection
tools.

@@

Most of the detection strategies used fall either in the 
\textit{logic/formalisation} or \textit{other} class.
The first one was probably overly broad since it included any solution using
inference rules engines, formalisation and semantic web ontologies.
Surprisingly, the latter strategy was the focus of many articles.

@@

The Gang of Four identified three design pattern types: creationnal,
behavioural and structural patterns.
Due to the nature of each pattern types, it is usally aknowledged that
structural patterns should be easier to detect than behavioural patterns and
that the later are easier than creationnal patterns (citation needed). 
It was expected that this ordering would appear in the number of articles
associated with each pattern types. 
However, we can see that the detection of behavioural patterns has been the
subject of more articles than the two others.

@@

This can be explained either by the fact that structural design patterns
detection is considered as an easy problem, thus less likely to be the main
focus of a research paper or by the possibility is that behavioural design
patterns are in fact easier to detect than structural ones.
However, we believe the first possibilty to be more likely.

\subsection{Language dependance}
The majority of techniques are language dependant and the most used 
languages are Java and C++

@@

Acknowledgement

>>>>

Design patterns are best practices proposed by the Gang of Four in their seminal
book to recurring design problems.

@@

Detection of design patterns in software has been a relatively active research
interest of the past decade in software engineering.
Proposed methods of automatic detection aims in part to facilitate the work of
developers in understanding a piece of software through reverse engineering.

@@

No studies have been conducted to analyze the trends of the field.

@@

We decided to query only one database, Scopus \cite{c2}, that claims to be the
largest abstract and citation database of peer-reviewed literature.
It indexes the main Computer Science databases : Springer, IEEE, ACM and
others.
The main advantage of using Scopus is that it provides a functionality to
export the result of a search query on its database.
Some of those exported results would not have been easily obtainable on some
publishers search engines that do not provide an export functionality.
Consequently, Scopus was used mostly as a Search and Export portal over the
relevant publications, greatly reducing the effort needed to extract the
original articles set. 
% TODO: Original articles set <- better wording?!

From the two research questions we tried to maximize the number of publications
found on the subject.
% Thesaurus is a synonym dictionnary... therefore a "disjunction of thesaurus"
% doesn't make any sense.
To achieve that purpose we used for the query a disjunction of thesaurus for
\textit{detection} on their respective contracted form : \textit{detect*},
\textit{recogni*} and \textit{ident*}.
We have then added to the query a disjunction of \textit{pattern} and \textit{motif}.
The query was limited to the abstract, the title, and keywords of each article.
% Do we like oxford comma?

@@

The query resulted in a total of 403 articles.
Of those articles, we found two duplicates that were immediately removed from
the set of articles to analyze which brings down the number of articles for
screening to 401.

@@

It is usually said that a Cohen's kappa coefficient of more than $0.7$ indicate
a good agreement.% citation needed

@@

\begin{itemize}
  \item \textbf{Detection strategy}:
    This determine the means on which the detection is based.
    Possible values: Artificial intelligence, Logic/Formalization, Graph,
    Metric, Automata, Instrumentation/profiling and Others.

  \item \textbf{Language dependence}:
    This category aims to classify detection methods on whether it is dependent
    on the language or not. 
    Possible values: Dependant or Independent
% This  specifies if the detection is langage dependent or independent,

@@

  \item \textbf{Detected pattern types}:
    This characterizes the type of design pattern a specific detection method
    can manage.
    The possible values for this category are Creational, Behavioral,
    Structural and Not specified.

@@

\begin{center}
  \begin{tabular}{ lll }
    \bf Category & \bf Class & \bf \# of articles \\
    \hline
    \multirow{7}{*}{Detection Strategy}
    & \multicolumn{1}{l}{AI}           & \multicolumn{1}{l}{11} \\
    & \multicolumn{1}{l}{Logic}        & \multicolumn{1}{l}{22} \\
    & \multicolumn{1}{l}{Graph}        & \multicolumn{1}{l}{15} \\
    & \multicolumn{1}{l}{Metric}       & \multicolumn{1}{l}{7} \\
    & \multicolumn{1}{l}{Automata}     & \multicolumn{1}{l}{1} \\
    & \multicolumn{1}{l}{Instr./Prof.} & \multicolumn{1}{l}{10} \\
    & \multicolumn{1}{l}{Pattern Matching}
                                       & \multicolumn{1}{l}{8} \\
    & \multicolumn{1}{l}{Others}       & \multicolumn{1}{l}{23} \\
    \hline
    \multirow{2}{*}{\textbf{Language Dependence}}
    & \multicolumn{1}{l}{Dependant}    & \multicolumn{1}{l}{XXX} \\
    & \multicolumn{1}{l}{Independent}  & \multicolumn{1}{l}{XXX} \\
    \hline
    \multirow{3}{*}{\textbf{Analysis Type}}
    & \multicolumn{1}{l}{Static}       & \multicolumn{1}{l}{XXX} \\
    & \multicolumn{1}{l}{Dynamic}      & \multicolumn{1}{l}{XXX} \\
    & \multicolumn{1}{l}{Hybrid}       & \multicolumn{1}{l}{XXX} \\
    \hline
    multirow{3}{*}{Detection Level}
    & \multicolumn{1}{l}{Execution}    & \multicolumn{1}{l}{8} \\
    & \multicolumn{1}{l}{Source}       & \multicolumn{1}{l}{44} \\
    & \multicolumn{1}{l}{Model}        & \multicolumn{1}{l}{7} \\
    \hline
    \multirow{2}{*}{Pattern detection generality}
    & \multicolumn{1}{l}{Specific}     & \multicolumn{1}{l}{XXX} \\
    & \multicolumn{1}{l}{General}      & \multicolumn{1}{l}{XXX} \\
    \hline
    \multirow{4}{*}{Detected Pattern Types}
    & \multicolumn{1}{l}{Creational}  & \multicolumn{1}{l}{23} \\
    & \multicolumn{1}{l}{Structural}   & \multicolumn{1}{l}{34} \\
    & \multicolumn{1}{l}{Behavior}    & \multicolumn{1}{l}{49} \\
    & \multicolumn{1}{l}{Other/Not Specified}
                                       & \multicolumn{1}{l}{17} \\
    \hline
    \multirow{6}{*}{Validation Method}
    & \multicolumn{1}{l}{Benchmark}    & \multicolumn{1}{l}{7} \\
    & \multicolumn{1}{l}{Case Study}   & \multicolumn{1}{l}{40} \\
    & \multicolumn{1}{l}{Experiment}   & \multicolumn{1}{l}{8} \\
    & \multicolumn{1}{l}{Survey}       & \multicolumn{1}{l}{0} \\
    & \multicolumn{1}{l}{Other}        & \multicolumn{1}{l}{1} \\
    & \multicolumn{1}{l}{None}         & \multicolumn{1}{l}{11}
  \end{tabular}
\end{center}

@@

This could indicate either that the field is mature and that research avenues
has been satisfied, that the field currently hit a roadblock, or that interest
is fading due to a lack of interest in the need for design pattern detection
tools.

@@

Most of the detection strategies used fall either in the 
\textit{logic/formalization} or \textit{other} class.
The first one was probably overly broad since it included any solution using
inference rules engines, formalization and semantic web ontologies.
Surprisingly, the latter strategy was the focus of many articles.

@@

The Gang of Four identified three design pattern types: creational,
behavioral and structural patterns.
Due to the nature of each pattern types, it is usually acknowledged that
structural patterns should be easier to detect than behavioral patterns and
that the later are easier than creational patterns (citation needed). 
It was expected that this ordering would appear in the number of articles
associated with each pattern types. 
However, we can see that the detection of behavioral patterns has been the
subject of more articles than the two others.

@@

This can be explained either by the fact that structural design patterns
detection is considered as an easy problem, thus less likely to be the main
focus of a research paper or by the possibility is that behavioral design
patterns are in fact easier to detect than structural ones.
However, we believe the first possibility to be more likely.

\subsection{Language dependence}
The majority of techniques are language dependent and the most used 
languages are Java and C++

@@

Acknowledgment
